---
title: "Safe Driver Missing Data"
author: "Anastasia Vishnyakova"
date: "`r format(Sys.time(), %d %B %Y)`"
output: 
  html_document:
    code_folding: hide
---

Import data

```{r setup, include=FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen=999)


# install.packages(c('tidyverse', 'missForest', 'purrr', 'forcats', 'Matrix', 'doParallel', 'Hmisc', 'xgboost', 'caret'))


library(tidyverse)
library(missForest)
library(purrr)
library(knitr)
library(forcats)
library(Matrix)
library(doParallel)
library(Hmisc)
library(xgboost)
library(caret)


# train <- read_csv("train.csv", na = c('-1', '-1.0')) %>%
#   mutate_at(vars(matches("bin|cat|target")), funs(factor))
#   
# test <- read_csv('test.csv', na = c('-1', '-1.0')) %>%
#     mutate(target = NA)%>%
#   mutate_at(vars(matches("bin|cat|target")), funs(factor))



library(dummies)
library(forcats)
library(Matrix)
library(doParallel)


library(caret)

library(Amelia)
library(VIM)
library(mice)
library(ggthemes)
library(broom)

library(plotly)
library(vcd)
library(ggmosaic)



train <- read_csv("train.csv", na = c('-1', '-1.0')) %>%
  mutate_at(vars(matches("bin|cat|target")), funs(factor))
  
test <- read_csv('test.csv', na = c('-1', '-1.0')) %>%
    mutate(target = NA)%>%
  mutate_at(vars(matches("bin|cat|target")), funs(factor))


```

Add levels for missing data categorical variables. 

```{r}

# train <- train %>%
#   mutate_at(vars(ps_car_03_cat, ps_car_05_cat, ps_car_07_cat), funs(fct_explicit_na(., na_level = "missing"))) %>%
#   mutate(ps_reg_03_cat_m = factor(ifelse(is.na(ps_reg_03), 1, 0)),
#          ps_car_14_cat_m = factor(ifelse(is.na(ps_car_14), 1, 0)))
# 
# 
# test <- test %>%
#   mutate_at(vars(ps_car_03_cat, ps_car_05_cat, ps_car_07_cat), funs(fct_explicit_na(., na_level = "missing"))) %>%
#   mutate(ps_reg_03_cat_m = factor(ifelse(is.na(ps_reg_03), 1, 0)),
#          ps_car_14_cat_m = factor(ifelse(is.na(ps_car_14), 1, 0)))
# 
# 
# save(train, file = 'train.Rda')
# save(test, file = 'test.Rda')


#load Rda files after transformations are complete
load('train.Rda')
load('test.Rda')

```


Impute missing values with random forest

```{r}

train <- train %>%
  mutate_at(vars(ps_car_03_cat, ps_car_05_cat, ps_car_07_cat), funs(fct_explicit_na(., na_level = "missing"))) %>%
  mutate(ps_reg_03_cat_m = factor(ifelse(is.na(ps_reg_03), 1, 0)),
         ps_car_14_cat_m = factor(ifelse(is.na(ps_car_14), 1, 0)))


test <- test %>%
  mutate_at(vars(ps_car_03_cat, ps_car_05_cat, ps_car_07_cat), funs(fct_explicit_na(., na_level = "missing"))) %>%
  mutate(ps_reg_03_cat_m = factor(ifelse(is.na(ps_reg_03), 1, 0)),
         ps_car_14_cat_m = factor(ifelse(is.na(ps_car_14), 1, 0)))
```


Impute missing values with random forest, excluding the ps_car_11_cat (needs grouping)

```{r}

#create dummy variables from a category with too many values
registerDoParallel(cores = detectCores()-1)

registerDoParallel(cores = 4)


train_mf <- missForest(as.data.frame(train %>% 
                           select(-id, - target, -ps_car_14_cat_m, - ps_reg_03_cat_m, - ps_car_11_cat) %>%
                           bind_cols(as.data.frame((model.matrix(target ~ ps_car_11_cat, data = train))) %>%
                                       select( - `(Intercept)`))
                           ) %>% sample_n(1000)
                       ,
                       verbose = TRUE, 
                       ntree = 500,
                       parallelize = 'forests'
                       )

vars_missing <- train %>% 
  select(which(colMeans(is.na(.))>0)) %>% 
  colnames()

train_mf <- train %>%
  select(- one_of(vars_missing)) %>%
  bind_cols(
    train_mf$ximp %>%
  select(vars_missing) 
  )

save(train_mf, "train_mf.Rda")

#process test data 
test_mf <- missForest(as.data.frame(test %>% 
                           select(-id, - target, -ps_car_14_cat_m, - ps_reg_03_cat_m, - ps_car_11_cat) %>%
                           bind_cols(as.data.frame((model.matrix(target ~ ps_car_11_cat, data = test))) %>%
                                       select( - `(Intercept)`))
                           ) # %>% sample_n(1000)
                       ,
                       verbose = TRUE, 
                       ntree = 500,
                       parallelize = 'forests'
                       )

test_mf <- test %>%
  select(- one_of(vars_missing)) %>%
  bind_cols(
    test_mf$ximp %>%
  select(vars_missing) 
  )

save(test_mf, "test_mf.Rda")



```

Impute missing values with medians and most popular category

```{r}


catvars <- train %>% 
  select(which(colMeans(is.na(.))>0))%>%
  select(matches("bin|cat")) %>% 
  colnames()


nvars <- train %>% 
  select(which(colMeans(is.na(.))>0))%>%
  select(-one_of(catvars)) %>%
  colnames()


train_simp <- train %>%
  mutate_at(vars(nvars), funs(impute(., mean)))%>%
  mutate_at(vars(catvars), funs(impute(., 'random'))) %>%
  select(which(colMeans(is.na(.))>0))
save(train_simp, file = 'train_simp.Rda')
  

test_simp <- test %>%
  mutate_at(vars(nvars), funs(impute(., mean)))%>%
  mutate_at(vars(catvars), funs(impute(., 'random'))) %>%
  select(which(colMeans(is.na(.))>0))
save(test_simp, file = 'test_simp.Rda')

```




Impute missing values with hmisc
```{r}


#create dummy variables from a category with too many values, exclude near zero vars

#train data 
areg_formula <- as.formula(paste0(paste(" ~ "), 
                           train %>% 
                             select(-id, - target, -ps_car_14_cat_m, - ps_reg_03_cat_m, - ps_car_11_cat, - ps_calc_04, - one_of(nzv$var)) %>%
                             colnames() %>%
                             paste(collapse = " + ")))


train_areg <- aregImpute(formula = areg_formula, 
                         nk = 0,
                         data = train %>% 
                           select(-id, - target, -ps_car_14_cat_m, - ps_reg_03_cat_m, - ps_car_11_cat, - ps_calc_04, - one_of(nzv$var)) #%>% sample_n(100000)
                         )


train_areg <- train %>%
  select(-one_of(vars_missing))%>%
  bind_cols(
    as.data.frame(impute.transcan(train_areg, 
                                  imputation=1, 
                                  data= train %>% 
                                    select(-id, - target, -ps_car_14_cat_m, - ps_reg_03_cat_m, - ps_car_11_cat, - ps_calc_04, - one_of(nzv$var)) %>%
                                    select(vars_missing), 
                                  list.out=TRUE, 
                                  pr=FALSE, 
                                  heck=FALSE))
  )

save(train_areg, file = 'train_areg.Rda')



#test data
test_areg <- aregImpute(formula = areg_formula, 
                         nk = 0,
                         data = test %>% 
                           select(-id, - target, -ps_car_14_cat_m, - ps_reg_03_cat_m, - ps_car_11_cat, - ps_calc_04, - one_of(nzv$var)) #%>% sample_n(100000)
                         )


test_areg <- test_mf %>%
  select(-one_of(vars_missing))%>%
  bind_cols(
    as.data.frame(impute.transcan(test_areg, 
                                  imputation=1, 
                                  data= test %>% 
                                    select(-id, - target, -ps_car_14_cat_m, - ps_reg_03_cat_m, - ps_car_11_cat, - ps_calc_04, - one_of(nzv$var)) %>%
                                    select(vars_missing), 
                                  list.out=TRUE, 
                                  pr=FALSE, 
                                  heck=FALSE))
  )

save(test_areg, file = 'train_areg.Rda')



```

Fit an xgboost model with one missing data imputed by random forest. Use parameters from a model trained by the team.

```{r}
train <- train %>% 
  filter(complete.cases(.)) 
  
dtrain <- xgb.DMatrix(data  = model.matrix( ~ .+0, 
                                 data = train %>% 
                                select( -target, - id, - ps_reg_03_cat_m, - ps_car_14_cat_m), 
                                with = FALSE),
                      label = as.numeric(train$target)-1)


test <- test %>% 
  filter(complete.cases(.)) 
  

dest <- xgb.DMatrix(data  = model.matrix( ~ .+0, 
                                 data = test %>% 
                                select( -target, - id, - ps_reg_03_cat_m, - ps_car_14_cat_m), 
                                with = FALSE))

xgb_rm <- xgboost(data = dtrain, 
               # label = as.numeric( train$target)-1, 
               max_depth = 2, #15, 
               eta = 1, # 0.01, 
               nthread = 2, 
               nrounds = 2, #25, 
               subsample = 1, #0.5,
               colsample_bytree = 0.5,
               eval_metric = "error",
               objective = "binary:logistic")


ypred_mf <- predict(xgb_mf, dtest)

save(ypred_mf, file = 'ypred_mf.R')



```











=======
                           ), 
                       verbose = TRUE, 
                       ntree = 500,
                       parallelize = "forests"
                       )



?missForest

```

>>>>>>> ead55fe520e9c3c00ae04b41a15006ebd74a44e7
