---
title: "Safe Driver EDA"
author: "Anastasia Vishnyakova"
date: "`r format(Sys.time(), %d %B %Y)`"
output: 
  html_document:
    code_folding: hide
---



```{r setup, include=FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen=999)

library(tidyverse)
library(Amelia)
library(VIM)
library(mice)
library(ggthemes)
library(broom)
library(purrr)
library(knitr)
library(plotly)
library(vcd)
library(ggmosaic)
library(forcats)
library(caret)
library(GGally)


train <- read_csv("train.csv", na = c('-1', '-1.0')) %>%
  mutate_at(vars(matches("bin|cat|target")), funs(factor))
  
test <- read_csv('test.csv', na = c('-1', '-1.0')) %>%
    mutate(target = NA)%>%
  mutate_at(vars(matches("bin|cat|target")), funs(factor))

  
```
#EDA for Safe Driver Data

This document presents EDA for Safe Driver data. 

##Exploration

###Train Data

```{r}

summary(train)

```

###Test Data

```{r}

summary(test)

```

###Missing Data

Missing Data Pattern: % of observations missing only 1, 2, 3, etc. values 
```{r}

as.matrix(table(rowSums(is.na(train)))/dim(train)[1])

```


VIM visualization for train data

```{r}

train %>%
  select(which(colMeans(is.na(.))>0)) %>%
  aggr()



  
```

VIM visualization for test data

```{r}
test %>%
  select(which(colMeans(is.na(.))>0), - target) %>%
  aggr()
  
```

Missing Data table. ps_car_03, ps_car_05, ps_reg_03 are missing a high proportion of values. Action could be to create a missing value category in the first two and impute the third variable. 

```{r, assis = TRUE}
kable(
test %>%
  mutate(source = 'test')%>%
  bind_rows(train %>% 
              mutate(source = 'train'))%>%
  select(which(colMeans(is.na(.)) > 0), source, - target) %>% 
  group_by(source)%>%
  summarise_all(funs(mean(is.na(.))*100)) %>%
  gather(variable, pctmissing, - source) %>%
  spread(source, pctmissing) %>%
  arrange(desc(train)),
caption = "Percent of Missing Values by Variable")
  
```



Encode missing values in categorical variables that have a high share of missing data. Create indicator categorical variables for numerical data with missing values.

```{r}
train <- train %>%
  mutate_at(vars(ps_car_03_cat, ps_car_05_cat, ps_car_07_cat), funs(fct_explicit_na(., na_level = "missing"))) %>%
  mutate(ps_reg_03_cat_m = factor(ifelse(is.na(ps_reg_03), 1, 0)),
         ps_car_14_cat_m = factor(ifelse(is.na(ps_car_14), 1, 0)))


test <- test %>%
  mutate_at(vars(ps_car_03_cat, ps_car_05_cat, ps_car_07_cat), funs(fct_explicit_na(., na_level = "missing"))) %>%
  mutate(ps_reg_03_cat_m = factor(ifelse(is.na(ps_reg_03), 1, 0)),
         ps_car_14_cat_m = factor(ifelse(is.na(ps_car_14), 1, 0)))
```


###Association Plots with Target vs. Categorical

```{r}

CreateAssociationPlots <- function(vars){
  data <- train %>%
    select_("response" = "target", 
             "predictor" = vars)
  assoc(table(data$predictor, data$response), shade = TRUE, main = vars)
}

vars <- train %>%
  select(matches('bin|cat'), -id, - target)%>%
  colnames() %>% 
  as.list() 

map(vars, CreateAssociationPlots)


```



###Logistic Models for Each Covariate

```{r, asis = TRUE}

def_nested_df <- function(x) {
    data_frame("covariate" = x,
               "data" = list(train %>% 
                               tbl_df %>%
                               select_("response" = "target", 
                                       "predictor" = x)))
  } 

kable(
train %>%
  select (one_of(unlist(vars)))  %>%
  colnames() %>%
  map_df(def_nested_df) %>%
  mutate(models = map(data, ~ glm(response ~ predictor, data = ., family = 'binomial')))%>%
  unnest(map(models, tidy))
)


 
```

###Logistic Models for Each Numerical Covariate

```{r}

kable(
train %>%
  select (-one_of(unlist(vars)), -id, - target)  %>%
  colnames() %>%
  map_df(def_nested_df) %>%
  mutate(models = map(data, ~ glm(response ~ predictor, data = ., family = 'binomial')))%>%
  unnest(map(models, tidy)) %>%
  filter(term == 'predictor' & p.value < 0.05) %>%
  arrange(desc(abs(estimate))),
caption = 'Selected Logistic Regression Output for Numerical Variables'
)


```

Visualize Distribution of Numeric Variables Across Target 

```{r}
#boxplots

CreateBoxplots <- function(vars){
  data <- train %>%
    select_("response" = "target", 
             "predictor" = vars)
    ggplot(data, aes(x = response, y = predictor)) +
    geom_boxplot()+
    theme_tufte() +
    ggtitle(vars)
}

nvars <- train %>%
  select(-one_of(unlist(vars)), -id, - target)%>%
  colnames() %>% 
  as.list() 

map(nvars, CreateBoxplots)


```

Density for numerical Variables across Target Variable 

```{r}
CreateDensityplots <- function(vars){
  data <- train %>%
    select_("response" = "target", 
             "predictor" = vars)
  print(vars)
    ggplot(data, aes(predictor, color = response)) +
    geom_line(stat = 'density', adjust = 1)+
    theme_tufte() +
    ggtitle(vars)
}


nvars <- map_df(train, class)%>%
  gather(measure, class)%>%
  filter(class == 'numeric') %>%
  select(measure) %>%
  .$measure %>%
  as.list(nvars)

map(nvars, CreateDensityplots)


```




Near Zero Variance Predictors using Caret

```{r}
kable(
  (nzv <- train %>%
  select(-id, - target)%>%
  nearZeroVar(saveMetrics = TRUE)%>%
  mutate(var = row.names(.))%>%
  filter(nzv))
  ,
  caption = 'Near Zero Variance Predictors')

save(nzv, file = 'nzv.Rda')

```



Correlations between Predictors

```{r}

(desc_cor <- train%>%
              select(unlist(nvars), -id, -one_of(nzv$var)) %>%
              cor(use = "pairwise.complete.obs")
)


train %>%
  select(unlist(nvars), -id, -one_of(nzv$var))%>%
  ggcorr(geom = "blank", label = TRUE, hjust = 0.75) +
  geom_point(size = 10, aes(color = coefficient > 0, alpha = abs(coefficient) > 0.5)) +
  scale_alpha_manual(values = c("TRUE" = 0.25, "FALSE" = 0)) +
  guides(color = FALSE, alpha = FALSE)

```

Find Linear Dependencies

```{r}

train %>%
  select(unlist(nvars), -id, -one_of(nzv$var), - ps_reg_03)%>%
  filter(complete.cases(.)) %>%
  findLinearCombos()



```




















